\tool

### 2018-04-04 paper/paper.tex
More updates from reading group feedback

\begin{abstract}
To increase software engineer productivity, toolsmiths create tools and features to automatically complete software development tasks. However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness. This paper introduces \tool, an automated recommendation system created for researchers to increase awareness of their products by making recommendations to developers on online collaboration websites. To help improve tool adoption among software engineers, \tool~uses a novel approach and original design principles to integrate concepts of user-to-user suggestions and industry practices in tool recommendations to developers, and our results suggest this approach is more effective in making tool recommendations to software developers on GitHub repositories.
\end{abstract}
\keywords{Tool Recommendations; Tool Discovery;}

@@

To keep up with rising demands for technology, software engineers emphasize \textit{software quality}. Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, buggy code remains a problem. The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity. The National Institute of Standards and Technology reports software engineers spend 70-80\% of work time debugging and the average time to debug one error is 17.4 hours~\cite{NIST}. Fixing defects early in the development process is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs. These tools can automatically perform a wide variety of software development tasks to save time and effort for developers. Additionally, the Software Engineering Body of Knowledge recommends using development tools because they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}. Utilizing software enginering tools can reduce software errors and debugging costs while increasing developer productivity.

Although quality is a concern for developers and users, many helpful software engineering tools go unused by developers. One of the primary barriers to tool adoption is the discoverability barrier, where users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}, compared to other modes of tool discovery~\cite{MurphyHill2011PeerInteraction}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

@@

To evaluate \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on the GitHub\footnote{https://github.com} code hosting platform. We calculated the effectiveness of \tool~by measuring the frequency of recommendations and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

@@

Previous work has also explored the tool discovery problem and barriers preventing users from adopting new tools, specifically in the software engineering industry. Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues studied the challenges of adopting these research-of-the-shelf tools in industry~\cite{Tilley2003ROTS}. Johnson and colleagues reported reasons why software engineers don't use static analysis tools to help find and prevent bugs in their code~\cite{Johnson2013Why}. Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}. Our project aims to increase tool discovery and adoption among developers by automatically recommending useful software enginering tools.

@@

\tool~aims to increase discovery and adoption of useful software engineering tools by implementing three design pillars: \textit{commend}, \textit{apprehend}, and \textit{recommend}.

@@

Previous research peer interactions influenced our three design pillars for \tool.

\subsection{Peer Interactions}
Previous research shows that recommendations between colleagues are the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently in the workplace but are more effective than system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.

To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks. They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics such as politeness and persuasiveness do not significantly impact the outcome of a suggestion~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

Previous work emphasizes the importance of user receptiveness. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior. Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.

\subsubsection{Desire}

A key desire of software users is to have enjoyable and problem-free experiences with software. Producers of software applications also have a similar desire to create high-quality functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. \tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

@@

>>>>

\begin{abstract}
To increase software engineer productivity, toolsmiths create tools and features to automatically complete software development tasks. However, these useful tools are often undiscovered or ignored by developers which is problematic for software applications that rely on programmer efficiency and correctness. This paper introduces \tool, an automated recommendation system designed for researchers to increase awareness of their products by making recommendations to developers. To help improve tool adoption among software engineers, we developed implemented a novel approach and design principles that integrate concepts of user-to-user suggestions and industry practices in \tool, and our results suggest this approach is more effective in making tool recommendations compared to other styles.
\end{abstract}
\keywords{Tool Recommendations; Tool Discovery;}

@@

To keep up with rising demands for technology, software engineers emphasize \textit{software quality}. Throughout the software development life cycle, development teams monitor code metrics that impact expectations of software producers and consumers~\cite{KitchenhamQualityTarget}. However, despite increased attention to software quality, buggy code remains a problem and the number of defects in software is increasing~\cite{HaveThingsChanged}. The Software Fail Watch by Tricentis suggests software failures impacted 3.7 billion users and caused \$1.7 trillion in financial losses in 2017.\footnote{https://www.tricentis.com/software-fail-watch/} Additionally, the process of finding and fixing bugs, or debugging, is a time-consuming and costly activity. The National Institute of Standards and Technology reports software engineers spend 70-80\% of work time debugging and the average time to debug one error is 17.4 hours~\cite{NIST}. Fixing defects early in the development process is also important since studies show debugging costs increase the longer a bug remains in code~\cite{SEEconomics, SoftwareAssuranceSDLC}.

To improve code quality and prevent errors, researchers and toolsmiths have created software engineering tools to aid developers in their work. Prior work shows that tools for static analysis~\cite{UsingStaticAnalysis}, refactoring~\cite{Murphy-HillFitness}, security, and more are beneficial for improving code and preventing bugs. These tools can automatically perform a wide variety of software development tasks to save time and effort for developers. Additionally, the Software Engineering Body of Knowledge recommends using development tools because they can be used to achieve ``desirable characteristics of software products''~\cite{SWEBOK}. Software enginering tools are useful for reducing software errors and debugging costs while increasing developer productivity.

Although software quality is important, development tools created to improve code are often ignored~\cite{Ivanov2017Gaps}. Previous work explores barriers preventing software engineers from adopting new tools: Tilley and colleagues studied challenges of adopting research-off-the-shelf tools in industry~\cite{Tilley2003ROTS}; Johnson and colleagues reported reasons why software engineers don't use static analysis tools~\cite{Johnson2013Why}; and Xiao and colleagues examined barriers of using security tools to prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}. One of the main barriers to tool adoption is the discoverability barrier, where users are unaware tools exist~\cite{Murphy-HillScreencastingDiscovery}. Lack of software engineering tool usage can lead to poor code quality, inconvenienced users, and significant amounts of time and money spent fixing errors. Many existing automated approaches have been implemented to increase awareness of software tools and features, but Murphy-Hill and colleagues found that developers prefer learning about tools from colleagues during normal work activities, or \textit{peer interaction}~\cite{MurphyHill2011PeerInteraction}.

@@

To implement our approach for \tool, we conducted a study making recommendations for \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool, to developers on GitHub\footnote{https://github.com}, a popular code hosting website. We measured the effectiveness of \tool~by observing the frequency of recommendations, rate of true and false positive recommendations, and how developers react to receiving suggestions from our system. This research makes the following contributions:

@@

@@

\tool~uses three design pillars to increase adoption of useful software engineering tools among developers: \textit{commend}, \textit{apprehend}, and \textit{recommend}.

@@

Our three design pillars for \tool~were inspired by previous research in tool recommendations.

\subsection{Peer Interactions}

Research suggests recommendations between colleagues is the most effective mode of tool discovery. Murphy-Hill and colleagues interviewed software engineers and found that, even though peer interactions occur less frequently in the workplace, developers prefer these user-to-user recommendations over system-to-user interactions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}.

To better understand what makes peer interactions an effective mode of tool discovery, Brown and colleagues observed how software users recommend tools to each other while completing tasks to study characteristics of peer interactions. Their results suggest \emph{receptiveness} is a significant factor in determining the outcome of a tool recommendation, while other characteristics such as politeness and persuasiveness are not as important~\cite{vlhcc17}. Fogg argues that a receptive audience is vital for designing persuasive technology, and defines receptiveness as: 1) demonstrating a desire and 2) familiarity with a target behavior~\cite{FoggPersuasive}. Below we explain how our design pillars for \tool~to recommend programming tools to software developers based on their desire and familiarity.

\subsubsection{Demonstrate Desire}

Software developers and users both desire high-quality code without errors. This desire is demonstrated by the fact software engineers spend the majority their time testing and debugging code~\cite{NIST}. Our \textit{commend}

\tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

@@

Don't mention Error Prone or GitHub until here (other than intro).
